Box 1 - TDT Curves

### 2023-09-21 ms/ms.qmd
Udpated doc

A number of significance challenges imped are ability to take the TDT and sub-lethal frameworks into a comparative context. First, ethical, conservation, and logistical challenges limit our ability to measure and estimate key parameters for many species, creating significant gaps in our knowledge across the tree of life. Second, while there has been a focus on species-level responses, population-level information is seldom incoperated into comparative frameworks limiting our ability to decompose sources of variance.

@@

We integrated static lethal limits ($CT_{max}$) collected by @Heerwaarden2021 and XX with dynamic lethal limit measures from TDT curces [i.e., slope ($z^{TDT}$) and intercept ($CT_{max}^{TDT}$)] estimated by XX. We also collected data to estimate TDT curve parameters for eight additonal species following protocols outlined in @Orsted2022. Critical fertility limits for *Drosophilids* were compiled from @Parratt2021 and @Heerwaarden2021. These data were integrated with data on lethal limits at the species-level. When the same species were sampled multiple times we retained within species variation in models. We then fit the following model in *MCMCglmm* [@]:

$$
\begin{bmatrix}
 CT_{max} \\
 CT_{max}^{TDT} \\
 z^{TDT} \\
 CFL
\end{bmatrix} = u_{i,k} + p_{i,k} + sp_{i,k} + e_{i,k}
$$

>>>>

A number of significant challenges imped are ability to take the TDT and sub-lethal frameworks into a comparative context. First, ethical, conservation, and logistical challenges limit our ability to measure and estimate key parameters for many species, creating significant gaps in our knowledge across the tree of life. Second, while there has been a focus on species-level responses, population-level information is seldom incoperated into comparative frameworks limiting our ability to decompose sources of variance [@Pottier2023].

@@

We integrated static lethal limits ($CT_{max}$) collected by @Heerwaarden2021 and XX with dynamic lethal limit measures from TDT curces [i.e., slope ($z^{TDT}$) and intercept ($CT_{max}^{TDT}$)] estimated by XX. We also collected data to estimate TDT curve parameters for eight additonal species following protocols outlined in @Orsted2022. Critical fertility limits for *Drosophilids* were compiled from @Parratt2021 and @Heerwaarden2021. These data were integrated with data on lethal limits at the species-level. When the same species were sampled multiple times we retained within species variation in models. We then fit the following model in R (vers. `r paste0(R.Version()$major, ".", R.Version()$minor)`)[@R2023] with the package *MCMCglmm* (vers. `r utils::packageVersion("MCMCglmm")`) [@Hadfield2010]:

$$
\begin{bmatrix}
 CT_{max} \\
 CT_{max}^{TDT} \\
 z^{TDT} \\
 CFLs
\end{bmatrix} = u_{i,k} + p_{i,k} + sp_{i,k} + e_{i,k}
$$
